MSE and dynamic state variable model with sigma function

### 2018-06-27 doc/MSE_MAR_18.tex
fixed changes in figures

\section{Introduction}
\label{sec1}

@@

\section{Methods}
\label{sec2}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.55\textwidth]{Figures/MSE.eps} 
\caption{The Managament Strategy Evaluation framework including the Operating Model (OM) and the Management Procedure (MP).}
\label{fig:MSE}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=0.4\textwidth]{Figures/Areadynamics.eps} 
\caption{The Operating Model (OM) including the key processes in the dynamics of the fish populations and how it was mapped.}
\label{fig:stockdyn}
\end{figure}

\subsection{Population dynamics}
\label{sec2.1}

In order to allow the fishery to make spatial and temporal choices, the model needed to be seasonally and spatially explicit. The dynamics of the fish stocks were modelled using an age-structured model that was spatially explicit, with seasonal time steps. In each seasonal time step, fish grow, migrate, and die. The number of fish of stock $i$ of age $a$ at year $y$, in season $s$, and area $p$ was written as $N_i (a, y, s, p)$.  The ages in the model range between age 0 and age $A$, the maximum age in the model. the seasons range between season 1 and season $S$, the last season within each year. Individuals were born at age 0, at the start of each year $y$, in season 1. The number of new-born individuals $R_i (p)$ in the model was a function of the area $p$ and independent of the size of the adult population. The population numbers at age 0 are thus

@@

\subsection{fleet dynamics}
\label{sec2.2}

@@

The maximum expected utility between current season $s$ and the end of the year was $V (L_i, Q_i, F_i, s)$, and the model started by setting $V (C_i, Q_i, F_i, S)= \Phi (C_i, Q_i, F_i)$. For preceding seasons, the expected utility depended on individual choices, and each time step individuals chose to visit fishing area $p$, or to stay in port.While fishing, any combination of the age classes caught of the quota species can be landed, or discarded. This discarding was defined by a matrix $d$. The size of that matrix was defined by the number of species under quota constraints and the number of age classes. Each element could take the value 0 (discard) or 1 (keep on board and land). The expected utility for each state and each time step $s$ was calculated backward using stochastic dynamic programming \cite{ClarkandMangel2000}:
\begin{equation}
V (C_i, Q_i, F_i, s) = max_{p,d}( R(p, d, s)- G(p) - C(p) + E_{p, d}[V (C_i^\prime, Q_i, F_i, s+1])),
\end{equation}

where $R(p, d, s)$ was the expected immediate contribution of the gross revenue from the sales of fish in a season resulting from choices $p$, and $d$ (gross revenues resulted from multiplying catches different age classes of species 1, species 2 and prices). Prices of fish were assumed to be dependent over fish age (subsection \ref{sec2.2.1}). $G(p)$ represented the incurred fuel costs per season from the choice of fishing area $p$, while  $ C(p)$ represented the variable operating costs (crew share, gear maintenance and landing costs, Table~\ref{t:fishery}), which in turn depended on the change in cumulative landings and fish prices. The term $E_{p, d}[V (C_i^\prime, Q_i, F_i, s+1]$ denoted the expected future utility taken over all possible states resulting from choices $p$, and $d$. The transition of these states were based on normal distributions of catch rates, using the means and variances for the species, as explained in the model conditioning section, following \cite{Poos2010}.

Rather than assuming that each individual always made the optimal choice, we assigned a probability to each choice proportional to its expected utility, following \cite{Dowling2011}. The expected utility for any choice was
\begin{equation}
U (C_i, Q_i, F_i, s) = R(p, d, s)- G(p) - C(p) + E_{p, d}[V (C_i^\prime, Q_i, F_i, s+1]).
\end{equation}

@@

Once the backward calculations were finished, the forward part is a Monte Carlo simulation where the probabilities of choices were sampled randomly using the probabilities in~\ref{eq:solve}. For each year, these forward Monte Carlo Simulations determine the fishing effort in each season and area $E(y,s,p)$, and the catches $C_i (a, y, s, p)$ for each age in each season and area

@@

maximum age                                                            & $A$                    & 6               \\
number of areas                                                       &                            & 2               \\
number of seasons                                                   & $S$                     & 6               \\
natural mortality                                                       & $M_i$                 & 0.0001     \\
Asymptotic length                                                    &  $L_{\infty_i}$   & 50            \\
Growth rate                                                              & $K_i$                 &  0.4          \\
Length-weight conversion factor                             & $ \alpha_i$        &  0.00005   \\
Length-weight isomorphy factor                              & $\beta_i $         &   3              \\
Migration                                                   & $D_i $         &   5\%              \\
&               \\
\textbf{Fleet dynamics}                                           &               \\ \hline   
&  \\%& & \\

Number of vessels                                                    &                       & 700           \\ 
Fuel costs (Euro fishing season\textsuperscript{-1})               &                       & 100        \\ 
Gear maintenance (Euro fishing season\textsuperscript{-1})  &                       & 50               \\ 
Crew share                                                               &                       & 35\%        \\ 
Landing costs (Euro t\textsuperscript{-1})              &                       & 0               \\
Optimal choice error                                                 & $\sigma $       & 40             \\

@@

Intial quota                                                               &                       & 200 \\%& & \\
catchability                                                               & $q_i (a)$        & 0.0005        \\ 
effort (p,s)                                                               &                       & 1                 \\ 
Price of species at mean weight                               & $\bar{p}_i$   & 150             \\
Slope of species price                                              & $\gamma_i$   &  100            \\
Fine for overshooting quota                                    &  $F_i$            & 3e6              \\
Ratio of standard deviations to catch means          & $\eta$           & 0.08           \\ 
&                 \\  \hline%& & \\\hline
\end{tabular}
}
\end{table}

\subsubsection{Size dependent pricing}
\label{sec2.2.1}
Prices of fish were assumed to be fixed over time but influenced by the body weight of the individuals in the catch, as is commonly observed \cite{Zimmermann2011, Zimmermann2013}. Following \cite{Zimmermann2011}, therelationship between fish price and body weight was modelled as:  
\begin{equation}
 p_i (a,s) = \bar{ p}_i + \gamma_i \times \frac{w_i (a,s) -\bar{w_i}}{\bar{w_i}},
\end{equation}
where $p_i (a,s) $ is the price of species $i$ at age $a$ and season $s$. The price was a linear function of the weight of individuals of species $i$ at age $a$ and season $s$. $\bar{p}_i$ is the price of the species at the mean weight over the age range. The mean weight over the age range is $\bar{w_i}$. $\gamma_i$ gave the price increase when individual mass was increased by $\bar{w_i}$.

@@

To mimic spatially heterogeneous fish populations in a mixed fishery where fishers make sequential choices on fishing areas and discarding patterns, the model was divided into a 'north' and 'south' area, and six fishing seasons per year (Table \ref{t:fishery}). There were two fish species in the model, both of which are caught by the fishery. The annual number of newborns is equal for the two species, and arbitrarily set to 400 per year. The species differ with respect to their nursery grounds: all individuals of species 1 are born in the southern area, while all individuals of species 2 are born in the northern area. The maximum age that any individual can reach was 4 years old. During their life, individuals grew in length towards the asymptotic length, which was 50 cm (Figure \ref{f:prices}). for both species. Conversion from length to weight was also equal for the two species (Table \ref{t:fishery}). Migration was parameterized so that a gradual diffusion occurred between the two areas, euqal to 20 percent of the difference in abundance. For the unfished situation this led to a clear segregation of the younger ages over the two areas, while the older ages were equally distributed over the two areas  (Figure \ref{f:distributions}). Mortality from natural causes such as predation, diseases, and senescence was assumed to be negligible, and $M_i$ set to 0.0001. Although such absence of natural mortality impossible in reality, one could argue that the model thus mimicked long-lived species.

Age-dependent catchability links the population biomasses to the catches in the fishery, and is thus one of the crucial parameters determining the interaction between the two. In the case study, this age-dependent catchability $q_i (a)$ was assumed independent of age $a$, and equal for the two species.

The mean prices for the two species were set to 150 euro per ton, ranging between 63 euro per ton for the youngest age and and 238 ton for the oldest age. The fines for overshooting the quota was set  to 500 euro per ton. These high fines combined with an assumed 100\% detection of exceeding quotas resulted in model results in which fishers comply with quota regulations.

\subsection{Management procedure}
\label{sec2.3}
The input to the fisheries model consist of the the expected catch rates and the individual quota that are set for each individual in the fleet. These individual quota are set in a management procedure, which mimics the decisions of a management body. this management body makes observations on the state of the resources, and the exploitation characteristics of the fishery. In the model, the management body is assumed to collect annual observations of the biomass of the stocks, including the distribution of the biomass over the different ages. these observations stem from fisheries independent observations, such as surveys with known catchabilities. In addition, the management body makes annual observations of the catches, including their age distribution. The observed biomass and catches allow for estimation of the annual harvest rates, and the estimation of a yield per recruit curve, that is dependent on fish growth and mortality. The yield curve is dome shaped, with a maximum that is called $H_{max}$. Fishing at a harvest rate that is equal to $H_{max}$  should lead to maximum sustainable yields. The yield per recruit curve omits the potential effect of the feedback between adult biomass and recruitment, which anyway is absent in the population dynamics, that assume a constant recruitment. The Harvest Control Rule used by the management body resuslts in annual quotas such that the harvest rate in a year corresponds to $H_{max}$. These quotas are then divided equally over the individual vessels in the simulations.

\subsection{Scenarios}
\label{sec2.4}
The model is set up in three consecutive time windows. In the first window of 10 years, newborns enter the population in the absence of fishing. This results in a virgin stock status. Then, the fleet of 700 vessels starts fishing in the absence of any fisheries regulations. This window lasts xxx years and gradually results in a situation where the stocks are overfished, i.e. the harvest rates are larger than $H_{max}$. Finally, the management procedure is started where the HCR controls the annual quotas.

The two management strategies we considered differ by the formulae used to determine exploitation rates (HCR). These management strategies were chosen such that, if  the  management  model  was  the  correct  model  of  reality,  the corresponding  equilibrium  state  of  the  system  would  meet  the  objective  of  the  plan. For this purpose, each strategy was implemented after a period where the fishery was unmanaged, by meaned with unconstrained quota for both species.

@@

The management model encompassed the harvest control rules (HCR). The HCR referenced to biological reference points (Fmsy) to produce management actions in the form of a harvest or effort level: changes in selectivity or spatial and temporal reallocations or restrictions of fishing effort. Costs and benefits, both economic and in terms of risks to both stock and livelihoods, could be computed and compared across different scenarios and management procedures (section \ref{sec2.3}).

\section{Results}
\label{sec3}

@@

\subsection{Catch decisions and location choice}
\label{sec3.1}
When discarding was allowed, but TACs changed by 15\% based on previous year but trying approximate to Fmsy, TACS showed a reduction and discards increased.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Effort.eps} 
\caption{Modelled spatial allocation of effort per year (\%) when (a) only species 1 has quota limitations and (d) both species are quota limited.  MP years reflect the year where the management plan was introduced. Panels (b-c) and (e-f) are the average monthly effort (days/month). Panels (b,e) are based on the 3 years monthly effort average (days) before the introduction of the MP, while (b,e) are the 3 years monthly effort average based on the period after the introduction of the MP.}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Economics.eps} 
\caption{Modelled main economics (thousand euro/ year) for the fleet under the management scenarios: (a-c) when the fishery is quota contrained only by species 1, while (d-f) both species constrained the fishery. Panels (a,d) and (b,e) shown the average annual net and grooss revenues, respectively, by vessel. MP year reflects the year where the management plan was introduced. Trade-offs between net revenue (black lline), gross revenue (grey line), fuel cost (blue line) and annual fines (red line) for the fleet are shown in panels (c,f).}
\end{figure}
%---

@@

\section{Discussion}
\label{sec4}
tbd
prellezo 2016, In the mid-term and without any consideration made in terms of the ecosystem functioning as a whole, the results obtained from applying any kind of exemption or flexibility are, simply, negative. Fishing beyond FMSY (even in one year) implies that there will be a penalty in the future. This penalty will come in the form of lower biomasses, that has the mixed effect of increasing the cost of fishing the same level of catches and reducing the total catch due to the lower abundances and the subsequent lower TACs.

>>>>

\section{Introduction}

@@

\section{Methods}

@@

\begin{figure}[!h]
\centering
\includegraphics[width=0.55\textwidth]{Figures/MSE.eps} 
\caption{Conceptual overview of the Managament Strategy Evaluation approach, including the Operating Model (OM) and the Management Procedure (MP) components of the framework.}
\label{fig:MSE}
\end{figure}

\begin{figure}[!h]
\centering
\includegraphics[width=0.4\textwidth]{Figures/Areadynamics.eps} 
\caption{The Operating Model (OM) component, including the key processes in the dynamics of the fish populations.}
\label{fig:stockdyn}
\end{figure}

\subsection{Population dynamics}

To allow the fishery to make spatial and temporal choices, the model needed to be seasonally and spatially explicit. The dynamics of the fish stocks were modelled using an age-structured model that was spatially explicit, with seasonal time steps. In each seasonal time step, fish grow, migrate, and die. The number of fish of stock $i$ of age $a$ at year $y$, in season $s$, and area $p$ was written as $N_i (a, y, s, p)$.  The ages in the model range between age 0 and age $A$, the maximum age in the model. The seasons range between season 1 and season $S$, the last season within each year. Individuals were born at age 0, at the start of each year $y$, in season 1. The number of new-born individuals $R_i (p)$ in the model was a function of the area $p$ and independent of the size of the adult population. The population numbers at age 0 are thus

@@

\subsection{Fleet dynamics}

@@

The maximum expected utility between current season $s$ and the end of the year was $V (L_i, Q_i, F_i, s)$, and the model started by setting $V (C_i, Q_i, F_i, S)= \Phi (C_i, Q_i, F_i)$. For preceding seasons, the expected utility depended on individual choices, and each time step individuals chose to visit fishing area $p$, or to stay in port. While fishing, any combination of the age classes caught of the quota species can be landed, or discarded. This discarding was defined by a matrix $d$. The size of that matrix was defined by the number of species under quota constraints and the number of age classes. Each element could take the value 0 (discard) or 1 (keep on board and land). The expected utility for each state and each time step $s$ was calculated backward using stochastic dynamic programming \cite{ClarkandMangel2000}:
\begin{equation}
V (C_i, Q_i, F_i, s) = max_{p,d}( R(p, d, s)- G(p) - C(p) + E_{p, d}[V (C_i^\prime, Q_i, F_i, s+1])),
\end{equation}

where $R(p, d, s)$ was the expected immediate contribution of the gross revenue from the sales of fish in a season resulting from choices $p$, and $d$ (gross revenues resulted from multiplying catches different age classes of species 1, species 2 and prices). Prices of fish were assumed to be dependent over fish age (subsection X). $G(p)$ represented the incurred fuel costs per season from the choice of fishing area $p$, while  $ C(p)$ represented the variable operating costs (crew share, gear maintenance and landing costs, Table~\ref{t:fishery}), which in turn depended on the change in cumulative landings and fish prices. The term $E_{p, d}[V (C_i^\prime, Q_i, F_i, s+1]$ denoted the expected future utility taken over all possible states resulting from choices $p$, and $d$. The transition of these states were based on normal distributions of catch rates, using the means and variances for the species, as explained in the model conditioning section, following \cite{Poos2010}.

Rather than assuming that each individual always made the optimal choice, we assigned a probability to each choice proportional to its expected utility, following \cite{Dowling2011}. The expected utility for any choice was
\begin{equation}
U (C_i, Q_i, F_i, s) = R(p, d, s)- G(p) - C(p) + E_{plaa, d}[V (C_i^\prime, Q_i, F_i, s+1]).
\end{equation}

@@

Once the backward calculations were finished, the forward part is a Monte Carlo simulation where the probabilities of choices were sampled randomly using the probabilities in~\ref{eq:solve}. For each year, these forward Monte Carlo Simulations determine the fishing effort in each season and area $E(y,s,p)$, and the catches $C_i (a, y, s, p)$ for each age in each season and area. The effort allocation component of the operating model provides the link between the management decisions and the biological component of the operating model.

@@

new-born individuals                                        & $R_i (p)$           & 500               \\
maximum age                                                 & $A$                 & 6               \\
number of areas                                             & $p$                 & 2               \\
number of seasons                                           & $S$                 & 12               \\
natural mortality                                           & $M_i$               & 0.0001     \\
Asymptotic length                                           & $L_{\infty_i}$      & 50            \\
Growth rate                                                 & $K_i$               &  0.6         \\
Length-weight conversion factor                             & $ \alpha_i$         &  0.0002   \\
Length-weight isomorphy factor                              & $\beta_i $          &   3              \\
Migration                                                   & $D_i $              &   2.5\%              \\
&               \\
\textbf{Fleet dynamics}                                     &               \\ \hline   
&  \\%& & \\

Number of vessels                                           &                       & 8000           \\ 
Fuel costs (Euro fishing season\textsuperscript{-1})        &                       & 0        \\ 
Gear maintenance (Euro fishing season\textsuperscript{-1})  &                       & 0               \\ 
Crew share                                                  &                       & 0\%        \\ 
Landing costs (Euro t\textsuperscript{-1})                  &                       & 0               \\
Optimal choice error                                        & $\sigma $             & 5000            \\

@@

Intial quota                                                &                       & 200 \\%& & \\
catchability                                                & $q_i (a)$             & 0.000025        \\ 
effort (p,s)                                                &                       & 1                 \\ 
Price of species at mean weight                             & $\bar{p}_i$           & 30000             \\
Slope of species price                                      & $\gamma_i$            &  1000            \\
Fine for overshooting quota                                 &  $F_i$                & 3e6              \\
Ratio of standard deviations to catch means                 & $\eta$                & 0.08           \\ 
&                 \\  \hline%& & \\\hline
\end{tabular}
}
\end{table}

\subsubsection{Size dependent pricing}

Prices of fish were assumed to be fixed over time but influenced by the body weight of the individuals in the catch, as is commonly observed \cite{Zimmermann2011, Zimmermann2013}. Following \cite{Zimmermann2011}, therelationship between fish price and body weight was modelled as:  
\begin{equation}
 p_i (a,s) = \bar{ p}_i + \gamma_i \times \frac{w_i (a,s) -\bar{w_i}}{\bar{w_i}},
\end{equation}
where $p_i (a,s) $ is the price of species $i$ at age $a$ and season $s$. The price was a linear function of the weight of individuals of species $i$ at age $a$ and season $s$. $\bar{p}_i$ is the price of the species at the mean weight over the age range. The mean weight over the age range is $\bar{w_i}$. $\gamma_i$ gave the price increase when individual mass was increased by $\bar{w_i}$.

To mimic spatially heterogeneous fish populations in a mixed fishery where fishers make sequential choices on fishing areas and discarding patterns, the model was divided into a 'north' and 'south' area, and twelve fishing seasons per year (Table \ref{t:fishery}). There were two fish species in the model, both of which are caught by the fishery. The annual number of newborns was equal for the two species, and arbitrarily set to 500 per year. The species differed with respect to their nursery grounds: all individuals of species 1 were born in the northern area, while all individuals of species 2 were born in the southern area (Figure \ref{f:distributions}). The maximum age that any individual can reach was 6 years old. During their life, individuals grew in length towards the asymptotic length, which was 50 cm for both species (Figure \ref{f:prices}). Conversion from length to weight was also equal for the two species (Table \ref{t:fishery}). Migration was parameterized so that a gradual diffusion occurred between the two areas, equal to 2.5 percent of the difference in abundance. For the unfished situation this led to a clear segregation of the younger ages over the two areas, while the older ages were equally distributed over the two areas (Figure \ref{f:distributions}). Mortality from natural causes such as predation, diseases, and senescence was assumed to be negligible, and $M_i$ set to 0.0001. Although such absence of natural mortality impossible in reality, one could argue that the model thus mimicked long-lived species.

Age-dependent catchability linked the population biomasses to the catches in the fishery, and was thus one of the crucial parameters determining the interaction between the two. In the case study, this age-dependent catchability $q_i (a)$ was assumed independent of age $a$, and equal for the two species.

The mean prices for the two species were set to 30 thousand euro per ton, ranging between 29 thousand euro per ton for the youngest age and 30.5 thousand ton for the oldest age (Figure \ref{f:prices}). The fines for overshooting the quota was set  to 3000 thousand euro per ton (Table \ref{t:fishery}). These high fines combined with an assumed 100\% detection of exceeding quotas resulted in model results in which fishers comply with quota regulations.

@@

\subsection{Management procedure}

The input to the fisheries model consisted of the the expected catch rates and the individual quota that were set for each individual in the fleet. These individual quota were set in a management procedure, which mimicked the decisions of a management body. This management body made observations on the state of the resources, and the exploitation characteristics of the fishery. In the model, the management body was assumed to collect annual observations of the biomass of the stocks, including the distribution of the biomass over the different ages. These observations stem from fisheries independent observations, such as surveys with known catchabilities. In addition, the management body made annual observations of the catches, including their age distribution. The observed biomass and catches allowed for estimation of the annual harvest rates, and the estimation of a yield per recruit curve, that was dependent on fish growth and mortality. The yield curve was dome shaped, with a maximum that is called $H_{max}$. Fishing at a harvest rate that is equal to $H_{max}$  should lead to maximum sustainable yields. The yield per recruit curve omited the potential effect of the feedback between adult biomass and recruitment, which anyway was absent in the population dynamics, that assumed a constant recruitment. The Harvest Control Rule used by the management body resuslted in annual quotas such that the harvest rate in a year corresponded to $H_{max}$. These quotas were then divided equally over the individual vessels in the simulations.

The management model encompassed the harvest control rules (HCR). The HCR referenced to biological reference points (Fmsy) to produce management actions in the form of a harvest or effort level: changes in selectivity or spatial and temporal reallocations or restrictions of fishing effort. Costs and benefits, both economic and in terms of risks to both stock and livelihoods, could be computed and compared across different scenarios and management procedures.

@@

\subsection{Scenarios}

The model was set up in three consecutive time windows. In the first window of 10 years, newborns entered the population in the absence of fishing. This resulted in a virgin stock status. Then, the fleet of 8000 vessels started fishing in the absence of any fisheries regulations. This window lasted 15 years and gradually resulted in a situation where the stocks were overfished, i.e. the harvest rates were larger than $H_{max}$. Finally, the management procedure started where the HCR controls the annual quotas.

The two management strategies we considered differ simply by the

formulae used to determine exploitation rates (HCR). These management strategies were chosen such that, if  the  management  model  was  the  correct  model  of  reality,  the corresponding  equilibrium  state  of  the  system  would  meet  the  objective  of  the  plan. For this purpose, each strategy was implemented after a period where the fishery was unmanaged, by meaned with unconstrained quota for both species.

The comparison among these scenarios resulted in the 
However, the  long term benefits to fisheries that could result from improved selectivity are ignored in those studies. Ignoring the potential for improved selectivity leaves out a key element in the perceived benefit of the LO. Because the LO should provide incentives for the use of more selective gears and for fisheries to  move away from areas with high levels of unwanted catch \cite{Alzorriz2016, Alzorriz2018}, the improved selectivity should lead to higher long term catches. Achieving single species MSY while landing all commercial catches in fisheries targeting multiple species (mixed fisheries) is challenging because achieving the objective for one species may mean missing the objective for another \cite{Batsleer2013,Ulrich2017}. Forecasting whether such management will be effective depends on understanding the response of individual effort allocation to the management.

\section{Results}

@@

\subsection{Catch decisions and location choice}

When discarding was allowed, but TACs changed by 15\% based on previous year but trying approximate to Fmsy, TACS showed a reduction and discards increased.

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Efforteconomics.eps} 
\caption{Modelled spatial allocation of effort per year (\%) when (a) only species 1 has quota limitations and (d) both species are quota limited.  MP years reflect the year where the management plan was introduced. Panels (b-c) and (e-f) are the average monthly effort (days/month). Panels (b,e) are based on the 3 years monthly effort average (days) before the introduction of the MP, while (b,e) are the 3 years monthly effort average based on the period after the introduction of the MP.}
\end{figure}

@@

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Meaneffort.eps} 
\caption{Modelled spatial allocation of effort per year (\%) when (a) only species 1 has quota limitations and (d) both species are quota limited.  MP years reflect the year where the management plan was introduced. Panels (b-c) and (e-f) are the average monthly effort (days/month). Panels (b,e) are based on the 3 years monthly effort average (days) before the introduction of the MP, while (b,e) are the 3 years monthly effort average based on the period after the introduction of the MP.}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=\textwidth]{Figures/Mean_Economics.eps} 
\caption{Modelled main economics (thousand euro/ year) for the fleet under the management scenarios: (a-c) when the fishery is quota contrained only by species 1, while (d-f) both species constrained the fishery. Panels (a,d) and (b,e) shown the average annual net and grooss revenues, respectively, by vessel. MP year reflects the year where the management plan was introduced. Trade-offs between net revenue (black lline), gross revenue (grey line), fuel cost (blue line) and annual fines (red line) for the fleet are shown in panels (c,f).}
\end{figure}
%---

@@

\section{Discussion}

tbd
prellezo 2016, In the mid-term and without any consideration made in terms of the ecosystem functioning as a whole, the results obtained from applying any kind of exemption or flexibility are, simply, negative. Fishing beyond FMSY (even in one year) implies that there will be a penalty in the future. This penalty will come in the form of lower biomasses, that has the mixed effect of increasing the cost of fishing the same level of catches and reducing the total catch due to the lower abundances and the subsequent lower TACs.
